---
title: |
  | **BIO144**  
  | Sheet 1
  |

author: |
  | Joel Fehr
  | 19-736-149
  |
date: "Date: xx.xx.xxxx"
output: pdf_document
fontsize: 16pt
header-includes: 

- \usepackage{titling}
- \usepackage{geometry}
- \usepackage{amsmath}
- \geometry{a4paper}
- \usepackage{graphicx}
- \usepackage{pdfpages}
- \usepackage{amsfonts}
- \usepackage{xcolor} %\textcolor{color}{text}
- \usepackage{pgfplots}
- \usepackage{framed}
- \usepackage{mdframed}
- \usepackage{sectsty} %for sans serif in titles
- \usepackage{tikz} % for drawing
- \usetikzlibrary{intersections}
- \usepackage[utf8]{inputenc} %für umlaute
- \usepackage{marginnote}
#- \renewcommand{\familydefault}{\sfdefault} %sans serif ganzes dokument
#- \usepackage{cmbright}
#- \usepackage[euler-digits,small]{eulervm}
- \usepackage{charter}



- \setlength{\droptitle}{-6em}

- \pretitle{
- \vskip 2em\hrule height 0.05cm \begin{flushleft}\Huge\sffamily}
- \posttitle{\par\end{flushleft}}


- \preauthor{\begin{flushleft}\large\scshape}
- \postauthor{\end{flushleft}\vskip 1em}

- \predate{\begin{flushleft}\scshape}
- \postdate{\end{flushleft}\vskip 2em\hrule height 0.05cm}

- \usepackage[headsepline,footsepline]{scrlayer-scrpage}%headtopline für linie oberhalb
- \pagestyle{scrheadings} %kopf und fusszeile
- \ihead{Joel Fehr}
- \chead{BIO144}
- \ohead{19-736-149}
- \cfoot{\pagemark}
- \ofoot{FS21}
- \allsectionsfont{\sffamily} %sf for sections
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\newcommand{\exercise}[1]{\begin{mdframed}[backgroundcolor=black!20]
	\begin{center}
	\Large{\textsf{#1}}
	\end{center}
\end{mdframed}}

\newcommand{\subexercise}[1]{\begin{mdframed}[backgroundcolor=black!20]
	\begin{center}
	\Large{\textsf{#1}}
	\end{center}
\end{mdframed}}

\newcommand{\abs}[1]{\left|#1\right|} 
\newcommand{\norm}[1]{\left\|#1\right\|} 
\newcommand{\hlg}[1]{\colorbox{green!20}{#1}} 
\newcommand{\hlb}[1]{\colorbox{blue!20}{#1}}
\newcommand{\hlr}[1]{\colorbox{red!20}{#1}}
\newcommand{\hly}[1]{\colorbox{yellow!20}{#1}}
\newcommand{\nd}[3]{#1\sim\mathcal{N}(#2,#3)} 
\newcommand{\pd}[2]{#1\sim\mathcal{P}ois(#2)} 
\newcommand{\ed}[2]{#1\sim\mathcal{E}xp(#2)} 
\newcommand{\cd}[2]{#1\sim\chi_{#2}^{2}}
\newcommand{\bd}[3]{#1\sim\mathcal{B}in(#2,#3)}

\newcommand{\numm}[3]{\noindent \tikz[] \filldraw[fill=#1,draw=#1] (0,0) circle (12pt) node[#2]{\Large{$#3$}};}



```{r include=FALSE}
library(extrafont)
library(ggplot2)
library(tidyverse)
font_import(pattern = "lmroman*") 
library(latex2exp)
library(ggthemes)
```

\exercise{Exercise 1}
\numm{black!20}{black}{a}

```{r}
x <- 1:10
y <- x^2
plot(x,y, main="Example",xlab = TeX('$\\alpha^2$'), family="LM Roman 10", "l", lty=2)
```
\pagebreak

\numm{blue}{white}{b}

$\nd{X_1}{\mu}{\sigma}$

```{r}
ggplot(data=iris, aes(y=Sepal.Length, x =Petal.Length, col = Species,
                      shape = Species)) +
	geom_point() +
	labs(title = "Introduction to ggplot2", subtitle = "but a short one", 
			 caption = "by Joël Fehr", tag="Plot 1",y= TeX('$\\frac{\\alpha}{\\beta^2}$'), 
			 x = TeX('$\\alpha^\\beta$'), legend= "Legend") +
	theme(legend.position="top",text=element_text(size=16,
	                                              family="serif")) 
# you can also use theme(legend.position = c(0.7, 0.2)
```

```{r}
p <- ggplot(data=mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(x = TeX('$\\a^2 + b^2 = c^2$'), title = 'Example')

p + geom_rangeframe() +
  theme_tufte()
```

