---
title: |
  | **BIO144**  
  | Week 1
  |

author: |
  | Joel Fehr
  | 19-736-149
  |
date: "Date: 26.02.2021"
output: pdf_document
fontsize: 16pt
header-includes: 

- \usepackage{titling}
- \usepackage{geometry}
- \usepackage{amsmath}
- \geometry{a4paper}
- \usepackage{graphicx}
- \usepackage{pdfpages}
- \usepackage{amsfonts}
- \usepackage{xcolor} %\textcolor{color}{text}
- \usepackage{pgfplots}
- \usepackage{framed}
- \usepackage{mdframed}
- \usepackage{sectsty} %for sans serif in titles
- \usepackage{tikz} % for drawing
- \usetikzlibrary{intersections}
- \usepackage[utf8]{inputenc} %für umlaute
- \usepackage{marginnote}
#- \renewcommand{\familydefault}{\sfdefault} %sans serif ganzes dokument
#- \usepackage{cmbright}
#- \usepackage[euler-digits,small]{eulervm}
- \usepackage{charter}



- \setlength{\droptitle}{-6em}

- \pretitle{
- \vskip 2em\hrule height 0.05cm \begin{flushleft}\Huge\sffamily}
- \posttitle{\par\end{flushleft}}


- \preauthor{\begin{flushleft}\large\scshape}
- \postauthor{\end{flushleft}\vskip 1em}

- \predate{\begin{flushleft}\scshape}
- \postdate{\end{flushleft}\vskip 2em\hrule height 0.05cm}

- \usepackage[headsepline,footsepline]{scrlayer-scrpage}%headtopline für linie oberhalb
- \pagestyle{scrheadings} %kopf und fusszeile
- \ihead{Joel Fehr}
- \chead{BIO144}
- \ohead{19-736-149}
- \cfoot{\pagemark}
- \ofoot{FS21}
- \allsectionsfont{\sffamily} %sf for sections
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\newcommand{\exercise}[1]{\begin{mdframed}[backgroundcolor=black!20]
	\begin{center}
	\Large{\textsf{#1}}
	\end{center}
\end{mdframed}}

\newcommand{\subexercise}[1]{\begin{mdframed}[backgroundcolor=black!20]
	\begin{center}
	\Large{\textsf{#1}}
	\end{center}
\end{mdframed}}

\newcommand{\abs}[1]{\left|#1\right|} 
\newcommand{\norm}[1]{\left\|#1\right\|} 
\newcommand{\hlg}[1]{\colorbox{green!20}{#1}} 
\newcommand{\hlb}[1]{\colorbox{blue!20}{#1}}
\newcommand{\hlr}[1]{\colorbox{red!20}{#1}}
\newcommand{\hly}[1]{\colorbox{yellow!20}{#1}}
\newcommand{\nd}[3]{#1\sim\mathcal{N}(#2,#3)} 
\newcommand{\pd}[2]{#1\sim\mathcal{P}ois(#2)} 
\newcommand{\ed}[2]{#1\sim\mathcal{E}xp(#2)} 
\newcommand{\cd}[2]{#1\sim\chi_{#2}^{2}}
\newcommand{\bd}[3]{#1\sim\mathcal{B}in(#2,#3)}

\newcommand{\numm}[3]{\noindent \tikz[] \filldraw[fill=#1,draw=#1] (0,0) circle (12pt) node[#2]{\Large{$#3$}};}



```{r include=FALSE}
library(extrafont)
library(ggplot2)
library(tidyverse)
font_import(pattern = "lmroman*") 
library(latex2exp)
library(ggthemes)
```

\section{Reaction time Male vs Female}

In this short report we try to find out if there is a significant difference in reaction times between Males and Females. We use data, which we have collectet in the lecture on monday.

```{r}
the_URL <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQFgYX1QhF9-UXep22XmPow1ZK5nbFHix9nkQIa0DzqUhPtZRxH1HtY-hsno32zDiuIHiLb2Hvphk1L/pub?gid=1188775314&single=true&output=csv"
class_RTs <- read_csv(the_URL)
names(class_RTs) <- c("Timestamp", "ID", "Gender", "Pref_Reaction_time_1",
                      "Verbal_memory_score", "Number_memory_score",
                      "Visual_memory_score",
                      "Weight_kgs", "Handed", "Nonpref_Reaction_time_ave",
                      "Pref_Reaction_time_2", "Pref_Reaction_time_3", 
                      "Pref_Reaction_time_4", "Pref_Reaction_time_5",
                      "Pref_Reaction_time", "Random_number")
class_RTs %>%
  group_by(Gender) %>%
  summarise(number = n())
```

```{r}
library(ggplot2)
library(gridExtra)
p1 <- ggplot(data=class_RTs, aes(x=Pref_Reaction_time_1)) +
  geom_histogram(binwidth = 30)
p2 <- ggplot(data=class_RTs, aes(x=Pref_Reaction_time_1)) +
  geom_histogram(binwidth=30) +
  facet_grid(.~Gender)
grid.arrange(p1,p2,nrow=2)
```

```{r}
p1 <- ggplot(data=class_RTs, aes(x=Gender, y=Pref_Reaction_time_1,color=Gender,alpha=Pref_Reaction_time_1)) +
  geom_jitter(width=0.05) + labs(alpha='Reaction time',title='Reaction time Female vs Male',y='Reaction time (seconds)')
p2 <- ggplot(data=class_RTs, aes(x=Gender, y=Pref_Reaction_time)) +
  geom_boxplot() +
  ylab("Reaction time (seconds)")
grid.arrange(p1,p2,ncol=2)
```

\vspace{1cm}

\exercise{Findings}

The last part of the exercise is to report your findings, including the direction and size of the difference in reaction times between males and females, and a measure of uncertainty in that difference.

\begin{itemize}
\item{The direction of the differences is than Females have a longer reaction time than males.}
\item{mean in females: $307.9606$ mean in males: $277.6809$}
\item{As we can see, the p-value is very low so it is unlikely to reach this result with the assuption that there is no difference between males and females in reaction time}
\item{The confidence interwall shows that we have a probability of $95 \%$ that the difference will be between $9.7$ and $50.8$ $ms$ in reaction time between males and females.}
\end{itemize}

